Reducing object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-09 paper/post_tci.tex
Changed k to p for specifying components of eigenvector and eigencoefficients in Eq.3

The prior is built by computing the covariance matrix from the
template set $\{Q_i\}_{i=1}^L$. The space spanned by the eigenvectors
$\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance
matrix is the object prior and is assumed to contain most of the test
slice (or volume in the case of 3D) that is similar, but not
necessarily identical to the object-prior. We use all of the $L-1$
orthogonal eigenvectors as a basis to represent the unknown test
volume. Let $\boldsymbol{\mu}$ denote the mean of the previously
scanned objects, and $\boldsymbol{\alpha}$ the unknown vector of
eigen-coefficients of the test scan, of which $\alpha_k$ is the
$k^{\textrm{th}}$ element. Then, once the eigenspace is pre-computed,
the test was reconstructed in~\cite{my_dicta_paper} by imposing a
penalty if the estimated slice does not lie within the eigen-space of
the object prior. Although such a prior can be very useful in some circumstances, it poses a limitation when we want accurate details of a portion of
the new changes. While the object prior compensates very well for the
possible artefacts due to sparse measurements, it may dominate the
regions with new changes masking the signal. \\

Ideally, we will want to
impose the prior only in the regions that are common between the test
and object-prior.  Our spatially-varying prior based reconstruction
overcomes this limitation by minimizing the following cost function:
\begin{equation}
  \begin{split}
%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
  J_3(\boldsymbol{x},\boldsymbol{\alpha}) = &\lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\\
  &\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
  \label{eq:spatially_varying_prior}
  \end{split}
\end{equation}

>>>>

The prior is built by computing the covariance matrix from the
template set $\{Q_i\}_{i=1}^L$. The space spanned by the eigenvectors
$\{\boldsymbol{V_p}\}_{p=1}^{L-1}$ (eigenspace) of the covariance
matrix is the object prior and is assumed to contain most of the test
slice (or volume in the case of 3D) that is similar, but not
necessarily identical to the object-prior. We use all of the $L-1$
orthogonal eigenvectors as a basis to represent the unknown test
volume. Let $\boldsymbol{\mu}$ denote the mean of the previously
scanned objects, and $\boldsymbol{\alpha}$ the unknown vector of
eigen-coefficients of the test scan, of which $\alpha_p$ is the
$p^{\textrm{th}}$ element. Then, once the eigenspace is pre-computed,
the test was reconstructed in~\cite{my_dicta_paper} by imposing a
penalty if the estimated slice does not lie within the eigen-space of
the object prior. Although such a prior can be very useful in some circumstances, it poses a limitation when we want accurate details of a portion of
the new changes. While the object prior compensates very well for the
possible artefacts due to sparse measurements, it may dominate the
regions with new changes masking the signal. \\

Ideally, we will want to
impose the prior only in the regions that are common between the test
and object-prior.  Our spatially-varying prior based reconstruction
overcomes this limitation by minimizing the following cost function:
\begin{equation}
  \begin{split}
%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
  J_3(\boldsymbol{x},\boldsymbol{\alpha}) = &\lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\\
  &\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{p}\boldsymbol{V_p}\alpha_p))\rVert_2^2.
  \label{eq:spatially_varying_prior}
  \end{split}
\end{equation}
